Draft Documents

### 2022-10-30 src/draft.Rmd
changes in draft structure
export countries data

---
title: "Draft Documents"
author: "Team 1 (Hedgehog, Callista, Imtiyaaz, Issac)"
date: "`r Sys.Date()`"
output: pdf_document
bibliography: citations.bib
---

@@

@@

These can be very useful and relevant information [@pubspend&pov]. However, we would like to exclude these variables from some first analyses to make use of the richer set of data. We can conduct a separate analysis with these variable to gain more insight.

@@

## 2.3. Descriptive Analytics
(To be done)
## 2.4. Data Source

>>>>

---
title: "Draft Documents"
author: "Team 1 (Hedgehog, Callista, Imtiyaaz, Issac)"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
bibliography: citations.bib
---

@@

# 1. Introduction (To be done)

@@

expenditure in primary, secondary, and tertiary edication can be very useful and relevant information to predict poverty reduction [@pubspend&pov]. However, we would like to exclude these variables from some first analyses to make use of the richer set of data. We can conduct a separate analysis with these variable to gain more insight.

@@

## 2.3. Descriptive Analytics (To be done)

## 2.4. Data Source
